Self-test prime dimensional EPR pairs with constant alphabet

### 2019-01-31 Draft/draft.tex
Honghao: generalized our result to work for prime numbers whose primitive root is 2, 3 or 5

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$ by explicitly giving the 
correlation that achieves this goal. Then the self-testing property of this correlation is 
given in the following theorem.
\begin{theorem}[Informal]
\label{thm:pr_2}
	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
	primitive root $2$, can be self-tested by a constant-sized correlation.
\end{theorem}
The correlation that we use to prove \cref{thm:pr_2} is denoted by $C(\dr{2})$.
We use the superscript $(2)$ to denote the primitive root of $d$.
Note that although the size of $C(\dr{2})$ does not depend on $d$, the optimal correlation does.
This correlation can be easily modified to self-test the maximally entangled state whose local dimension has 
primitive $3$ or $5$.

@@

We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/2}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity.
Through out this paper, any operation on the label of the eigenvector $\ket{i}$ is taken modulo $d$,
unless otherwise specified, for example, the $i/2$ above.

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $2$,
and this correlation is denoted by $C(\dr{2})$.
The correlation we constructed is the optimal correlation for a game $\G(\dr{2})$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
The main component of $\G(\dr{2})$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uxu^{-1} = x^2$.
\begin{proposition}
	\label{prop:embed}
	The group $\Pg$ can be embedded into a linear system game $\LS$ over $\Z_2$,
	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2}.

In the later parts of the paper, we use $n = 118$ and $m = 91$ to refer to the size of $\LS$.
The key feature of this embedding is that $\LS$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ can have arbitrary order. 
The product of the generators $x_1$ and $x_2$ from the solution group of $\LS$ plays the role 
of the generator $x$ in $\Pg$ and the product of the generators $x_3$ and $x_4$ plays the role
of the generator $u$ in $\Pg$. As shown in \cref{sec:power2}, $x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
\begin{align}
	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^2.
\end{align}
Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
the key relation that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^2\ket{\psi}, 
\end{align}
and similarly on Bob's side.
If we denote the unitary corresponding to the generator $u$ of $\Pg$ by $U$ and the unitary
corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
$UXU\ct \ket{\psi} = X^2 \ket{\psi}$.
The special property of $U$ and $X$ is summarized in the following lemma.

\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
	\end{align}
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

We start with proving that $\ket{x_{k_1}} = 0$.
Proving $\ket{x_{k_i}} = 0$ for other $i$ follows a similar argument, so we briefly
discuss about it in the end.
The entry $\bra{1}M\ket{1}$ can be expressed as  
\begin{align}
	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/2^k}\braket{i}{1}.
\end{align}
For the term $\braket{1}{i/2^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $2^k \equiv 1 \pmod{d}$, or equivalently,
$k = k_1$. Hence, we can conclude that 
\begin{align}
	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
\end{align}
Similarly we can determine that for all $j = 1,2\dots d-1$,
\begin{align}
	\bra{j}M\ket{j} 
	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/2^k}\braket{i}{j} 
	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
\end{align}
Hence we get $d-1$ equations with $d-1$ variables, and the linear system is
\begin{align}
	W \ket{x_{k_1}} = 0,
\end{align}
where $W_{m,n} = \omega_d^{mn}$. Then we define
\begin{align}
	\tW = 
	\begin{pmatrix}
	1 & 1 \\
	1 & W
	\end{pmatrix}.
\end{align}
First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
Next, we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
and prove that it satisfies the condition
that 
\begin{align}
	\tW \ket{\tx_{k_1}} = 0,
\end{align}
which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which is required by the first row of $\tW$.
It can be proved by summing the known $d-1$ equations as follows
\begin{align}
	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
	= \sum_{l = 1}^{d-1}- x_{k_1,l}
\end{align}
where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.

@@

To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
\end{proof}
%\begin{align}
%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
%\end{align}
%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
%by the following relations
%\begin{align}
%\label{eq:sim}
%	u_x x u_x = x^2, \quad
%	u_z z u_z = z^2.
%\end{align}
%Consequently, the $d$ dependency of $\G$ comes from constraints imposed by other components of the game,
%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
%relation $xzx^{-1}z^{-1} = \J$.
%
%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
%\begin{align}
%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
%\end{align}
%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
%we can verify that 
%\begin{align}
%	U_xU_z = \1 = U_zU_x,
%\end{align}
%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
%In the end, we define $\Pg_{\LS}$ by
%\begin{equation}
%\begin{aligned}
%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
%\end{aligned}
%\end{equation}
%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.

@@

The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
Alice and Bob's operator solution of $\LS$ has eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
$U$ and $X$ has the eigen-structure required by \cref{lm:ux_independ}.
We denote this game that enforces the eigenvalues of the observable $X$ by
$\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.

@@

%=====================================
\section{Main result}
\label{sec:main}
%=====================================
In this section, we introduce the correlation $C(\dr{2})$, which is the
ideal correlation of $\G(\dr{2})$, and then
prove that it can self-test the state $\ket{\EPR{d-1}}$.

%-----------------------------------------------------------------
\subsection{The correlation $C(\dr{2})$}
%-----------------------------------------------------------------
Assume the linear system game has $n=118$ variables and $m=91$ equations.
In game $\G(\dr{2})$, 
Alice receives $x \in \{1,\dots m+3 \}$ and Bob receives
$y \in \{1,\dots,n+1\}$. We follow the previous structure by first give intuition about how they should
behave in this game. The correlation can be easily extracted from the behaviour list below.
\begin{itemize}
	\item When $x \in \{1,\dots m\}$ and $y \in \{1, \dots n\}$, they should win the 
	linear system game $\LS$ perfectly;
	\item when $x \in \{m+1, m+2, m+3\}$ and $y \in \{1, 2, n+1\}$, they should follow the
	optimal correlation of the test $\CHSH_X$, where 
	\begin{align}
		&\ast_A = m+1, \quad 0_A = m+2,\quad 1_A = m+3,\\
		&\ast_B = n+1,\quad 0_B = 1, \quad 1_A = 2,
	\end{align}
	are the inputs for the game $\CHSH_X$
	(The intuition behind is that $B_1B_2 = X$.);
	\item otherwise, their behaviour is irrelevant.
\end{itemize}
Note that the dimension $\dr{2}$ is defined in the rules of $\CHSH_X$.

>>>>

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$ by explicitly giving the 
correlation that achieves this goal. Then the self-testing property of this correlation is 
given in the following theorem.
\begin{theorem}[Informal]
\label{thm:pr_2}
	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
\end{theorem}
The correlation that we use to prove \cref{thm:pr_2} is denoted by $C(\dr{r})$.
We use the superscript $(r)$ to denote the primitive root of $d$.
Note that although the size of $C(\dr{r})$ does not depend on $d$, the optimal correlation does.

@@

We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
and $r$ is the primitive root of $d$.
Through out this paper, any operation on the label of the eigenvector $\ket{i}$ is taken modulo $d$,
unless otherwise specified, for example, the $i/r$ above.

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $r \in \{2, 3, 5\}$,
and this correlation is denoted by $C(\dr{r})$.
The correlation we constructed is the optimal correlation for a game $\G(\dr{r})$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg_r= \langle u, x : uxu^{-1} = x^r \rangle, \text{ for } r \in \{2, 3,5\}.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uxu^{-1} = x^r$.
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS$ over $\Z_2$,
	with constant numbers of variables and equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

In the later parts of the paper, we use $n_r$ and $m_r$ to refer to the size of $\LS_r$.
The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ have arbitrary order. 
The product of the generators $x_1$ and $x_2$ from the solution group of $\LS_r$ plays the role 
of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
of the generator $u$ in $\Pg_r$. As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
$x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
\begin{align}
	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^r.
\end{align}
Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
the key relation that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^r\ket{\psi}, 
\end{align}
and similarly on Bob's side.
If we denote the unitary corresponding to the generator $u$ of $\Pg_r$ by $U$ and the unitary
corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
$UXU\ct \ket{\psi} = X^r \ket{\psi}$.
The special property of $U$ and $X$ is summarized in the following lemma.

\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/r}{i},
	\end{align}
	where $d$ is an odd prime number with primitive root $r$,
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^r$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

We start with proving that $\ket{x_{k_1}} = 0$.
Proving $\ket{x_{k_i}} = 0$ for other $i$ follows a similar argument, so we briefly
discuss about it in the end.
The entry $\bra{1}M\ket{1}$ can be expressed as  
\begin{align}
	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/r^k}\braket{i}{1}.
\end{align}
For the term $\braket{1}{i/r^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $r^k \equiv 1 \pmod{d}$, or equivalently,
$k = k_1$. Hence, we can conclude that 
\begin{align}
	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
\end{align}
Similarly we can determine that for all $j = 1,2\dots d-1$,
\begin{align}
	\bra{j}M\ket{j} 
	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/r^k}\braket{i}{j} 
	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
\end{align}
Hence we get $d-1$ equations with $d-1$ variables, and the linear system is
\begin{align}
	W \ket{x_{k_1}} = 0,
\end{align}
where $W_{m,n} = \omega_d^{mn}$. Then we define
\begin{align}
	\tW = 
	\begin{pmatrix}
	1 & 1 \\
	1 & W
	\end{pmatrix}.
\end{align}
First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
Next, we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
and prove that it satisfies the condition
that 
\begin{align}
	\tW \ket{\tx_{k_1}} = 0,
\end{align}
which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which is required by the first row of $\tW$.
It can be proved by summing the known $d-1$ equations as follows
\begin{align}
	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
	= \sum_{l = 1}^{d-1}- x_{k_1,l}
\end{align}
where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.

@@

To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
\end{proof}
Note that the primitive root $r$ in the lemma is not restricted to the set $\{2,3,5\}$, so this lemma works for any 
odd prime number $d$.

%\begin{align}
%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
%\end{align}
%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
%by the following relations
%\begin{align}
%\label{eq:sim}
%	u_x x u_x = x^2, \quad
%	u_z z u_z = z^2.
%\end{align}
%Consequently, the $d$ dependency of $\G$ comes from constraints imposed by other components of the game,
%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
%relation $xzx^{-1}z^{-1} = \J$.
%
%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
%\begin{align}
%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
%\end{align}
%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
%we can verify that 
%\begin{align}
%	U_xU_z = \1 = U_zU_x,
%\end{align}
%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
%In the end, we define $\Pg_{\LS}$ by
%\begin{equation}
%\begin{aligned}
%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
%\end{aligned}
%\end{equation}
%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.

@@

The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
Alice and Bob's operator solution of $\LS$ has eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
$X$ has the eigen-structure required by \cref{lm:ux_independ}.
We denote this game that enforces the eigenvalues of the observable $X$ by
$\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
We remark that for the extended weighted CHSH test, the primitive root of $d$ is irrelevant,
so we drop the superscript $(r)$.

@@

%=====================================
\section{Main result}
\label{sec:main}
%=====================================
In this section, we introduce the correlation $C(\dr{r})$, which is the
ideal correlation of $\G(\dr{r})$, and then
prove that it can self-test the state $\ket{\EPR{d-1}}$.

%-----------------------------------------------------------------
\subsection{The correlation $C(\dr{r})$}
%-----------------------------------------------------------------
Recall that the linear system game $\LS_r$ has $n_r$ variables and $m_r$ equations.
In game $\G(\dr{r})$, 
Alice receives $x \in \{1,\dots m_r+3 \}$ and Bob receives
$y \in \{1,\dots,n_r+1\}$. We follow the previous structure by first give intuition about how they should
behave in this game. The correlation can be easily extracted from the behaviour list below.
\begin{itemize}
	\item When $x \in \{1,\dots m_r\}$ and $y \in \{1, \dots n_r\}$, they should win the 
	linear system game $\LS_r$ perfectly;
	\item when $x \in \{m_r+1, m_r+2, m_r+3\}$ and $y \in \{1, 2, n_r+1\}$, they should follow the
	optimal correlation of the test $\CHSH_X$, where 
	\begin{align}
		&\ast_A = m_r+1, \quad 0_A = m_r+2,\quad 1_A = m_r+3,\\
		&\ast_B = n_r+1,\quad 0_B = 1, \quad 1_A = 2,
	\end{align}
	are the inputs for the game $\CHSH_X$
	(The intuition behind is that $B_1B_2 = X$.);
	\item otherwise, their behaviour is irrelevant.
\end{itemize}
Note that the dimension $\dr{r}$ is defined in the rules of $\CHSH_X$.

\begin{proposition}
	\label{prop:realize}
	The correlation $C(\dr{r})$ can be realized by a quantum strategy.
\end{proposition}
We prove this proposition by giving the ideal strategy.
\begin{proof}
The construction start with the ideal strategy for the weighted $\CHSH_X$ test.
We choose $\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1} \ket{ii}$ and $V = \spn(\ket{1} ,\ket{d-1})$.
Alice's projectors and observables for the weighted $\CHSH_X$ test are
\begin{align*}
	&A_\ast^\diamond = \ketbra{1}{1} + \ketbra{d-1}{d-1}, &&A_\ast^\perp = \1 - A_\ast^\diamond, \\
	&A_1 = A_1^0-A_1^1 = \ketbra{1}{1} - \ketbra{d-1}{d-1}, &&A_1^\perp = A_\ast^\perp,\\
	&A_2 = A_2^0-A_2^1 = \ketbra{1}{d-1} + \ketbra{d-1}{1} ,&&A_2^\perp = A_\ast^\perp.
\end{align*}
Bob's observables restricted to the subspace $V$ is
\begin{align*}
	B_1|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) - \sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}),\\
	B_2|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) +\sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}).
\end{align*}
To make sure operator $B_2$ commutes with the operator $U$ that we will construct later, we pick a 
special basis of $X =B_1B_2$, which is
\begin{align}
	\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{1} + i\ket{d-1}), &&
	\ket{x_{d-1}} = \frac{-e^{i\pi/d}}{\sqrt{2}}(\ket{1} - i\ket{d-1}).
\end{align}
It can be checked that $X\ket{x_1} = \omega_d \ket{x_1}$ and $X\ket{x_{d-1}} = \omega_d^{d-1} \ket{x_{d-1}}$.
In this basis, $B_1$ and $B_2$ are expressed as 
\begin{align}
	&B_1|_V = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
	&B_2|_V =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1}.
\end{align}
Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
the observables $B_1$ and $B_2$ are extended from $B_1|_V$ and $B_2|_V$ as follows
%\begin{align}
%	B_1 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/2d}\ketbra{x_{d-k}}{x_k}\right)\\
%	B_2 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_{d-k}}{x_k} + e^{-ik\pi/2d}\ketbra{x_{k}}{x_{d-k}}\right)
%\end{align}
\begin{align}
	B_1 &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
	B_2 &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
\end{align}
It can be checked that $B_1B_2 = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_i}{x_i}$ and the operator $U$ is
\begin{align}
	U = \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_i}.
\end{align}
The first step of the embedding procedure in the proof of \cref{prop:embed} requires
the commutativity between $U$ and $B_2$, which can be verified as follows,
\begin{align}
	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{i/r \pmod{d}}}{x_{(d-i)/r \pmod{d}}}.
\end{align}
Let $i_1 = i/r \pmod{d}$ and $i_2  = (d-i)/r \pmod{d}$, then
\begin{align*}
	i_1 + i_2 \equiv& \frac{i}{r} + \frac{d-i}{r} \pmod{d} \\
	\equiv& \frac{d}{r} \pmod{d}.
\end{align*}
Suppose $d/r \pmod{d} \equiv x$ for some integer $x$, then
\begin{align}
	rx \equiv d \pmod{d}.
\end{align}
Since $d$ is a odd prime number and $r < d$, then $r$ cannot divide $d$, so $x = 0$ or $d$.
Considering the fact that $1 \leq i_1 \leq d-1$ and $1 \leq i_2 \leq d-1$, we know $x = i_1+i_2 = d$.
Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
Now suppose for $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_i'}{x_{d-i'}}U\ct$,
it means that $i/r \equiv i'/r \pmod{d}$, which further implies that $i = i'$.
To conclude, conjugation by $U$ only permutes the terms of $B_2$, so
\begin{align}
	UB_2U\ct = B_2.
\end{align}
%There are two cases to consider which are the index is dividable by $r$ or not.
%Note that in the following calculation, the division is not with respect to the modulo $d$.
%When the index $i \equiv 0 \pmod{r}$, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{i/2}}{x_{d-i/r}}$, and
%when the index $i \not\equiv 0 \pmod{r}$, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{(d+i)/2}}{x_{(d-i)/2}}$,
%so we can calculate that 
%\begin{align}
%	\sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct 
%	=& \sum_{i=1}^{(d-1)/2}U\ketbra{x_{2i}}{x_{d-2i}}U\ct 
%	+ \sum_{i=0}^{(d-1)/2-1} U\ketbra{x_{2i+1}}{x_{d-(2i+1)}}U\ct\\
%	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=0}^{(d-1)/2-1} \ketbra{x_{(d+1)/2+i}}{x_{(d-1)/2-i}}\\
